Synthesizing Symmetric Lenses

### 2018-07-09 papers/SymmetricLenses/main.tex

% begin synthesis
\section{Synthesis}
\label{sec:synthesis}
Algorithm~\ref{alg:synth-sym-lens} presents our synthesis algorithm at a high
level of abstraction. The input regular expressions are first converted into
stochastic regular expressions with \ToStochastic. Once that conversion has
taken place, the we begin searching for the most likely lens. This search
itself is defined via five functions: (1) $\PCF{\PQ.Create}$, (2)
$\PCF{\PQ.Pop}$, (3) $\PCF{Expand}$, (4) $\PCF{\PQ.Push}$, and (5)
$\PCF{\Continue}$. First, $\PCF{\PQ.Create}$ creates a priority queue ($pq$)
containing a single element: the initial pair of stochastic regular expressions.
Next, $\PCF{SynthSymLens}$ enters a loop that searches for likely lenses. The
loop terminates when the algorithm believes it is unlikely to find a better lens
than the best one it has found so far (a termination condition defined by
$\PCF{\Continue}$). Within each iteration of the loop, it:
\begin{itemize}
\item generates the next class ($S$, $T$) of lenses to
search ($\PCF{\PQ.Pop}$),
\item executes $\GreedySynth$ to find a best lens in that class if
one exists ($\LC$),
using the examples $exs$ to filter out potential lenses that do not satisfy
the specification,
\item replaces $best$ with $\LC$, if $\LC$ has lower cost, and
\item adds all of the SREs derived from rewriting $S$ and $T$ ($\Expand(S,T)$)
  to the priority queue with $\PCF{\PQ.Push}$
\end{itemize}
When the loop terminates, the search returns the globally best lens found
($best$).  Each element of this algorithm will be explained in
further depth in the following subsections.

>>>>

% begin synthesis
\section{Synthesis}
\label{sec:synthesis}
Algorithm~\ref{alg:synth-sym-lens} presents our synthesis algorithm at a high
level of abstraction. The input regular expressions are first converted into
stochastic regular expressions with \ToStochastic.  
%Once that conversion has
%taken place, the $\RXSearch$ algorithm executes. This algorithm itself is
%defined via five functions: (1) $\PCF{\PQ.Create}$, (2) $\PCF{\PQ.Pop}$, (3)
%$\PCF{Expand}$, (4) $\PCF{\PQ.Push}$, and (5) $\PCF{\Continue}$. First,
This pair of SREs are used to initialize a priority queue ($pq$).
Next, $\PCF{SynthSymLens}$
enters a loop that searches for likely lenses. The loop terminates when the
algorithm believes it is unlikely to find a better lens than the best one it has
found so far (a termination condition defined by $\PCF{\Continue}$). Within each
iteration of the loop, it:
\begin{itemize}
\item pops the next class ($S$, $T$) of lenses to
search of the priority queue ($\PCF{\PQ.Pop}$),
\item executes $\GreedySynth$ to find a best lens in that class if
one exists ($\LC$),
using the examples $exs$ to filter out potential lenses that do not satisfy
the specification,
\item replaces $best$ with $\LC$, if $\LC$ has lower cost according
to our information theoretic metric, and
\item adds all of the SREs derived from rewriting $S$ and $T$ ($\Expand(S,T)$)
  to the priority queue with $\PCF{\PQ.Push}$
\end{itemize}
When the loop terminates, the search returns the globally best lens found
($best$).  Each element of this algorithm will be explained in
further depth in the following subsections.
